---
title: "What is going on with the binding site set?"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    highlight: zenburn
    self_contained: yes
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
    # number_sections: true
date: '`r Sys.Date()`'
author: 'Claire Rioualen'
---

```{r setup, include = FALSE}
setwd(".")
knitr::opts_chunk$set(echo = TRUE, include = TRUE, warning = FALSE, message = FALSE, cache = FALSE, eval = TRUE, results = 'asis', fig.width=10, fig.height=7, fig.align = 'left')

#------------------
library(DT)
library(readxl)
library(tidyverse)
#------------------
library(gridExtra)
library(patchwork)
library(ggpubr)
#------------------
library(UpSetR)
library(ComplexUpset)
library(viridis)
# library(GGally)
library(cowplot)
library(plotly)

source(file = "utils.r")

dir_releases <- "_Databases/RegulonDB/releases"
dir_results <- "_Results"

```

# BindingSiteSet.txt  {.tabset}

## Releases

Comparison of the BindingSiteSet.txt file between the last releases.

| Release version     | Date           |
|---------------------|----------------|
| 10.6                | 2019 July      |
| 10.6.3              | -              |
| 10.7                | 2020 April     |
| 10.8                | 2020 October   |
| 10.9                | 2021 April     |
| 10.10               | 2022 February  |
| 11.0                | 2022 August    |
| 11.0.1 (not public) | 2022 September |
| 11.0.2 (not public) | 2022 September |

Notes:

* V10.6 excluded because it doesn't include TU_ID, only TU names which are not unique; otherwise it's almost the same as v10.7 which is included
* Some formatting is done in order to uniformize columns accross versions (uppercase/lowercase in confidence levels, word or symbol +- for strand and effect, etc)
* Starting v11.0.1 there are 2 evidence columns (site evidence and function evidence), here I merged them so I can compare with older versions

Comments on evidence and confidence issues:

* Version 10.6 did not include confirmed TFBS **error query? corregido por Cesar en la versión 10.7**
* Version 10.7 seems right 
* Version 10.8 seem to have too many confirmed TFBSs: **erroneous cross-validations CV(SM) and CV(GEA) were added to all TFBS, sometimes even duplicated**
* Version 10.9 loses most evidence information: **?**
* Version 10.10 and 11.0 have mostly weak sites, and many NAs: **only function evidence is taken into account (not site)**
* Version 11.0.1 does not have confirmed TFBSs: **only site evidence is taken into account (not function)**
* Version 11.0.2 seems about right? **congruent with version 10.7**


```{r binding-sites-data-per-version}

## V10.6 excluded because it doesn't include TU_ID, only TU names which are not unique; otherwise it's almost the same as v10.7 which is included
## Some formatting is done in order to uniformize columns like strand and confidence (uppercase/lowercase, word or symbol +- for the strand, etc)
## Starting v11.0.1 there are 2 evidence columns, here I just merge them so I can compare with older versions

dir_versions <- c("10.7", "10.8", "10.9", "10.10", "11.0", "11.0.1", "11.0.2") 

tfbs_sets <- list()
tfbs_versions <- c()
for(v in dir_versions){
  version_tag <- paste0("v", v)
  set <- read.delim(paste0(dir_releases, "/", v, "/BindingSiteSet.tsv"), 
                    comment.char = "#", header = T, stringsAsFactors = F, na.strings = c("", "NA")) %>% 
    dplyr::mutate(version = version_tag) %>%
    dplyr::mutate(strand = ifelse(strand == "reverse", "-", ifelse(strand == "forward", "+", NA))) %>%
    dplyr::mutate(confidence = tolower(confidence)) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(evidence = ifelse("evidence_function" %in% colnames(.), concat_uniq2(evidence, evidence_function), evidence)) %>%
    dplyr::mutate(coords = paste0(start, "_", stop)) 
  
  assign(paste0("tfbs_set_", version_tag), set)
  tfbs_sets[[version_tag]] <- set
  tfbs_versions <- c(tfbs_versions, version_tag)
  
}
all_tfbs <- bind_rows(tfbs_sets) %>%
  dplyr::mutate(version = factor(version, levels =  tfbs_versions)) %>%
  dplyr::mutate(effect = factor(effect, levels =  c("+", "-", "?"))) %>%
  dplyr::mutate(confidence = factor(confidence, levels = c("weak", "strong", "confirmed")))

all_tfbs_by_evidence <- all_tfbs %>%
  tidyr::separate_rows(evidence, sep = ",") %>%
  dplyr::mutate(evidence = gsub("\\[|\\]", "", evidence)) %>% #,
  tidyr::separate(evidence, c("evidence_code", "evidence_level", "evidence_name"), sep = "\\|") 
```


## Overall number of TFBSs

```{r total-tfbs, fig.height=4, fig.width=6}
tfbs_summary <- all_tfbs %>%
  dplyr::group_by(version) %>%
  dplyr::summarise(total = n()) %>%
  dplyr::arrange(version)

TFBS_num <- simple_bar(tfbs_summary, "version", "total") +
  scale_fill_viridis(discrete = T) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "Release version", y = "Number of TFBSs", title = "")

TFBS_num

DT::datatable(tfbs_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```

Comments:

* Sudden increase with 488 new entries in version 10.9


## TFBS IDs 

### TFBS IDs shared between versions

```{r tfbs-ids-upset}
tfbs_ids <- list()
for (v in tfbs_versions) {
	tfbs_ids[[v]] <- unique( (get(paste0("tfbs_set_", v)))$TFBS_ID)
}
UpSetR::upset(fromList(tfbs_ids), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              queries = list(list(query = intersects, params = list("v10.7"), color = "red", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8"), color = "red", active = T),
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T))
              )
```

Comments:

* The oldest versions have **less** entries but **more** unique TFBS IDs
* 421 TFBS IDs **disappear** from version 10.8 until now (red bar)
* There are only 21 new IDs present in version 10.9 to 11.0.2 despite the sudden increase in total entries (blue bar)

### Duplicated TFBS IDs

```{r tfbs-ids-dupli}
tfbs_ids_dupli <- all_tfbs %>%
  dplyr::group_by(version, TFBS_ID) %>%
  dplyr::summarise(occurrences = n()) %>%
	  group_by(version, occurrences) %>% 
	  summarise(tfbs_number = n())%>%
  dplyr::mutate(occurrences = factor(occurrences))

###
dodge <- ggplot(tfbs_ids_dupli, aes(fill = occurrences, y = tfbs_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "", y = "Number of unique TFBS IDs", title = "TFBS ID duplication in BindingSiteSet.txt across versions")

dodge2 <- ggplot(tfbs_ids_dupli %>% dplyr::filter(!occurrences %in% c("1", "2", "3", "4")), aes(fill = occurrences, y = tfbs_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14),
        legend.position = "none") +
  labs(x = "", y = "Number of unique TFBS IDs", title = "...minimum 5 copies")

dodge / dodge2 

```

### Which TFBS IDs are most duplicated?

```{r which-dupli-tfbs-id}
## TFBS IDs that have at least 10 entries in a given version
tfbs_ids_dupli_max <- all_tfbs %>%
  dplyr::group_by(version, TFBS_ID) %>%
  dplyr::summarise(occurrences = n()) %>%
  dplyr::filter(occurrences >=10) %>%
  dplyr::arrange(desc(occurrences)) %>%
  pivot_wider(names_from = version,
              values_from = c(occurrences))

DT::datatable(tfbs_ids_dupli_max, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```


## Coordinates

```{r coords-shared}
coordinates <- list()
for (v in tfbs_versions) {
	coordinates[[v]] <- unique( (get(paste0("tfbs_set_", v)))$coords)
}
UpSetR::upset(fromList(coordinates), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              queries = list(
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8"), color = "red", active = T)
                             )
              )
```

```{r coords-dupli}
coords_dupli <- all_tfbs %>%
  dplyr::group_by(version, coords) %>%
  dplyr::summarise(occurrences = n()) %>%
	  group_by(version, occurrences) %>% 
	  summarise(coords_number = n())%>%
  dplyr::mutate(occurrences = factor(occurrences))

###
dodge <- ggplot(coords_dupli, aes(fill = occurrences, y = coords_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "", y = "Number of unique TFBS IDs", title = "TFBS ID duplication in BindingSiteSet.txt across versions")

dodge2 <- ggplot(coords_dupli %>% dplyr::filter(!occurrences %in% c("1", "2", "3", "4")), aes(fill = occurrences, y = coords_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14),
        legend.position = "none") +
  labs(x = "", y = "Number of unique TFBS IDs", title = "...minimum 5 copies")

dodge / dodge2 

```

### Which coordinates are most duplicated?

```{r which-dupli-coords}
## coords that have at least 10 entries in a given version
coords_dupli_max <- all_tfbs %>%
  dplyr::group_by(version, coords) %>%
  dplyr::summarise(occurrences = n()) %>%
  dplyr::filter(occurrences >=10) %>%
  dplyr::arrange(desc(occurrences)) %>%
  pivot_wider(names_from = version,
              values_from = c(occurrences))

DT::datatable(coords_dupli_max, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))
```


## Distance to TSS

```{r tfbs-dist-tss}
ggplot(all_tfbs, aes(x = distance_TSS, y = version, fill = version)) +
  ggridges::geom_density_ridges(color = "white") +
  ggridges::theme_ridges() + 
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme(legend.position = "none") +
  xlim(-1000, 1000)
```



## Distance to first gene

```{r tfbs-dist-gene}
ggplot(all_tfbs, aes(x = distance_gene, y = version, fill = version)) +
  ggridges::geom_density_ridges(color = "white") +
  ggridges::theme_ridges() + 
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme(legend.position = "none") +
  xlim(-1000, 1000)
```



## Effect

```{r tfbs-effect, fig.width=10}
tfbs_effect_long <- all_tfbs %>% 
  group_by(version, effect) %>% 
  summarise(value = n()) 

dodge <- ggplot(tfbs_effect_long, aes(fill = effect, y = value, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of TFBS", title = "")

stack <- ggplot(tfbs_effect_long, aes(fill = effect, y = value, x = version)) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of TFBS", title = "")

line <-  ggplot(tfbs_effect_long, aes(group = effect, y = value, x = version)) + 
  geom_line(aes(color = effect)) +
  geom_point(size = 2, aes(color = effect)) +
  scale_color_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "Release version", y = "Number of TFBS", title = "")

## ggplotly to make it interactive
# fig0 <- ggplotly(TFBS_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig1, fig2, fig3, nrows=3)
```


```{r tfbs-effect-summary}
effect_summary <- all_tfbs %>% 
  group_by(version, effect) %>% 
  summarise(value = n())  %>%
  data.frame() %>%
  pivot_wider(names_from = version, values_from = c(value)) %>%
   arrange(effect)

DT::datatable(effect_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```

## Evidence 

```{r tfbs-evidence}
tfbs_evidence_long <- all_tfbs_by_evidence %>% 
  group_by(version, evidence_code, evidence_name) %>% 
  summarise(value = n()) 

evidence_palette <- random_palette(length(unique(all_tfbs_by_evidence$evidence_code)))

##----
dodge <- ggplot(tfbs_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_name)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
    scale_fill_manual(values = evidence_palette, drop = F, na.value = "gray") +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of TFBSs", title = "")

stack <- ggplot(tfbs_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_name)) + 
  geom_bar(position = "stack", stat = "identity") +
    scale_fill_manual(values = evidence_palette, drop = F, na.value = "gray") +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of evidence", title = "")

line <-  ggplot(tfbs_evidence_long, aes(group = evidence_name, y = value, x = version)) + 
  geom_line(aes(color = evidence_code)) +
  scale_color_manual(values = evidence_palette, drop = F, na.value = "gray") +
  geom_point(size = 2, aes(color = evidence_code)) +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "Release version", y = "Number of TFBS", title = "")

fig0 <- ggplotly(TFBS_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig0, fig1, fig2, fig3, nrows=4)

```

```{r tfbs-evidence-table}
tfbs_evidence_table <- all_tfbs_by_evidence %>% 
  group_by(evidence_code, evidence_name) %>% 
  summarise(version = concat_uniq(version)) 

DT::datatable(tfbs_evidence_table, rownames= FALSE, options = list(searching = TRUE, lengthChange = FALSE, pageLength = 10))

```

```{r tfbs-evidence-upset}

tfbs_evidence_shared <- list()
for (v in tfbs_versions) {
	tfbs_evidence_shared[[v]] <- unique((all_tfbs_by_evidence %>% dplyr::filter(version == v))$evidence_code)
}

UpSetR::upset(fromList(tfbs_evidence_shared), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              # queries = list(list(query = intersects, params = list("v10.7"), color = "red", active = T),
              #                list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T))
              )

## Revise congruency between table and upset plot (table has CE listed as only present in 10.8, shjould have 10.7 too)
```


## Confidence 

```{r tfbs-confidence, fig.width=10}
tfbs_confidence_long <- all_tfbs %>% 
  group_by(version, confidence) %>% 
  summarise(value = n()) 

dodge <- ggplot(tfbs_confidence_long, aes(fill = confidence, y = value, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of TFBS", title = "")

stack <- ggplot(tfbs_confidence_long, aes(fill = confidence, y = value, x = version)) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of TFBS", title = "")

line <-  ggplot(tfbs_confidence_long, aes(group = confidence, y = value, x = version)) + 
  geom_line(aes(color = confidence)) +
  geom_point(size = 2, aes(color = confidence)) +
  scale_color_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "Release version", y = "Number of TFBS", title = "")

## ggplotly to make it interactive
# fig0 <- ggplotly(TFBS_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig1, fig2, fig3, nrows=3)
```


```{r evidence-level-tfbs-ta2b}
confidence_summary <- all_tfbs %>% 
  group_by(version, confidence) %>% 
  summarise(value = n())  %>%
  mutate(confidence = ifelse(is.na(confidence), "null", as.character(confidence))) %>%
  data.frame() %>%
  pivot_wider(names_from = version, values_from = c(value)) %>%
  mutate(across(starts_with('v'), ~replace_na(.,0))) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~"total"))) %>%
   mutate(confidence = factor(confidence, levels = c("weak", "strong", "confirmed", "null", "total"))) %>%
   arrange(confidence)

DT::datatable(confidence_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```


## RI IDs 

```{r ri-ids-mapping}
ri_ids <- list()
for (v in tfbs_versions) {
	ri_ids[[v]] <- unique( (get(paste0("tfbs_set_", v)))$RI_ID)
}
UpSetR::upset(fromList(ri_ids), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              queries = list(
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8", "v10.9", "v10.10"), color = "red", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8"), color = "red", active = T)
)
              )
```

### Duplicate RI IDs

```{r ris-ids-dupli}

ris_ids_dupli <- all_tfbs %>%
  dplyr::group_by(version, RI_ID) %>%
  dplyr::summarise(occurrences = n()) %>%
	  group_by(version, occurrences) %>% 
	  summarise(ris_number = n())%>%
  dplyr::mutate(occurrences = factor(occurrences))

###
dodge <- ggplot(ris_ids_dupli, aes(fill = occurrences, y = ris_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "", y = "Number of unique RI IDs", title = "RI ID duplication in BindingSiteSet.txt across versions")

dodge2 <- ggplot(ris_ids_dupli %>% dplyr::filter(!occurrences %in% c("1")), aes(fill = occurrences, y = ris_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14),
        legend.position = "none") +
  labs(x = "", y = "Number of unique RI IDs", title = "...minimum 2 copies")

dodge / dodge2 

```


## TFs

```{r tfs-shared, fig.height = 6}
tf_ids <- list()
for (v in tfbs_versions) {
	tf_ids[[v]] <- unique( (get(paste0("tfbs_set_", v)))$TF_ID)
}
UpSetR::upset(fromList(tf_ids), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TF IDs",
              queries = list(
                             list(query = intersects, params = list("v10.8", "v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T),
                             list(query = intersects, params = list("v10.7"), color = "red", active = T))
              )
tf_ids_gone <- rownames(fromList(tf_ids) %>% filter(v10.7 == 1 & v11.0.2 == 0))

tf_names <- list()
for (v in tfbs_versions) {
	tf_names[[v]] <- unique( (get(paste0("tfbs_set_", v)))$TF_name)
}
UpSetR::upset(fromList(tf_names), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TF names",
              queries = list(
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )

tf_names_gone <- rownames(fromList(tf_names) %>% filter(v10.7 == 1 & v11.0.2 == 0))

```

* 5 TF ID disappear: `r tf_ids_gone` (red)
* 2 TF names disappear: `r tf_names_gone` (red)


## Promoters

```{r promoter-shared}
promoter_name <- list()
for (v in tfbs_versions) {
	promoter_name[[v]] <- unique( (get(paste0("tfbs_set_", v)))$promoter)
}
UpSetR::upset(fromList(promoter_name), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique promoter names",
              queries = list(
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )
```


## TUs

```{r tus-shared, fig.height = 6}
tu_ids <- list()
for (v in tfbs_versions) {
	tu_ids[[v]] <- unique( (get(paste0("tfbs_set_", v)))$TU_ID)
}
UpSetR::upset(fromList(tu_ids), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TU IDs",
              queries = list(
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )


tu_names <- list()
for (v in tfbs_versions) {
	tu_names[[v]] <- unique( (get(paste0("tfbs_set_", v)))$TU_name)
}
UpSetR::upset(fromList(tu_names), sets = tfbs_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TU names",
              queries = list(
                             list(query = intersects, params = list("v10.8", "v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
                             list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )
```


## Mapping v10.7 vs v11.0.2

Notes:

* TFBSs from v10.7 and v11.0.2 are mapped by **TFBS_ID** and **promoter** name
  * TFBS_IDs are not unique, eg. a given TFBS_ID can be associated with several promoters and TUs
  * Some RI_IDs seem to have changed, all other parameters equal (ex. seems like Fis TFBS_ID ECK120011288 was associated with RI_ID ECK120034675, now ECK125300661)
  * Older versions of BindingSiteSet.txt did not come with a TU_ID column, and TU_name is not unique, and is sometimes missing

The following table displays the differences.
**Many (most?) differences seem to be caused by different promoter names**

Ex. 

* in 10.7 micFp is regulated by Lrp (TFBS ID ECK120011644)
* in 11.0.2 micFp1 and micFp2 are both regulated by the same TF and TFBS, and are linked to 2 distinct TUs (both TUs are named micF but have distinct IDs)
* **all three entries have the same evidence**


```{r tfbs-mapping}
## Join versions 10.7 and 11.0.2 by TFBS_ID and promoter name
tfbs_join_107_1102 <- tfbs_set_v10.7 %>%
  dplyr::full_join(tfbs_set_v11.0.2, by = c("TFBS_ID", "promoter"), suffix = c("_10.7", "_11.0.2")) %>%
  dplyr::arrange(TFBS_ID) %>%
  dplyr::select(TFBS_ID, promoter, starts_with("TF_name"), starts_with("TU"), starts_with("coords"), starts_with("evidence_1"), starts_with("confidence"))
  # select(TFBS_ID, promoter, everything())


tfbs_matches_107_1102 <- tfbs_join_107_1102 %>% na.omit

tfbs_differences_107_1102 <- dplyr::setdiff(tfbs_join_107_1102, tfbs_matches_107_1102)

write.table(tfbs_join_107_1102, file = paste0(dir_results, "/TFBS_full_join_107_1102.tsv"), quote = F, row.names = F, col.names = T, sep = "\t")
write.table(tfbs_differences_107_1102, file = paste0(dir_results, "/TFBS_differences_107_1102.tsv"), quote = F, row.names = F, col.names = T, sep = "\t")

DT::datatable(tfbs_differences_107_1102, rownames= FALSE, options = list(searching = TRUE, lengthChange = FALSE, pageLength = 5,
                                                                                columnDefs = list(list(width = '200px', targets = c(11,12)))
                                                                                ))
```

<!-- These are the entries that appear after version 10.8:  -->

```{r tfbs-frfom-10-9, eval = F, include = F}
tfbs_new_from_10.9 <- all_tfbs_RI_TU %>%
  dplyr::filter(is.na(evidence_10.6) & is.na(confidence_10.6) & 
                  is.na(evidence_10.6.3) & is.na(confidence_10.6.3) & 
                  is.na(evidence_10.7) & is.na(confidence_10.7) & 
                  is.na(evidence_10.8) & is.na(confidence_10.8))

write.table(tfbs_new_from_10.9, file = "TFBS_new_10.9.tsv", quote = F, row.names = F, col.names = T, sep = "\t")

# DT::datatable(tfbs_new_from_10.9, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 5))

```

<!-- These are the entries that are "confirmed" in version 10.8:  -->

```{r tfbs-confirmed-10-8, eval = F, include = F}
tfbs_confirmed_10.8 <- all_tfbs_RI_TU %>%
  dplyr::filter(confidence_10.8 == "Confirmed")

write.table(tfbs_confirmed_10.8, file = "TFBS_confirmed_10.8.tsv", quote = F, row.names = F, col.names = T, sep = "\t")

# DT::datatable(tfbs_confirmed_10.8, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 5))

```

# network_tf_gene.txt  {.tabset}

```{r network-tf-gene-data1}
dir_versions <- c("10.6.3", "10.7", "10.8", "10.9", "11.0", "11.0.1")
tfgnw_sets <- list()
tfgnw_versions <- c()

for(v in dir_versions){
  version_tag <- paste0("v", v)
  set <- read.delim(paste0(dir_releases, "/", v, "/network_tf_gene.tsv"), 
                    comment.char = "#", header = T, stringsAsFactors = F, na.strings = c("", "NA")) %>% 
    dplyr::mutate(effect = ifelse(effect == "repressor", "-", ifelse(effect == "activator", "+", ifelse(effect == "unknown", "?", effect)))) %>%
    dplyr::mutate(version = version_tag) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(evidence = ifelse("evidence_function" %in% colnames(.), concat_uniq2(evidence, evidence_function), evidence)) %>%
    dplyr::mutate(pairs = paste0(TF_name, "_", gene_name)) 

  
  assign(paste0("tfgnw_set_", version_tag), set)
  tfgnw_sets[[version_tag]] <- set
  tfgnw_versions <- c(tfgnw_versions, version_tag)
  
}
all_tfgnw <- bind_rows(tfgnw_sets) %>%
  dplyr::mutate(version = factor(version, levels =  tfgnw_versions)) %>%
  dplyr::mutate(effect = factor(effect, levels =  c("+", "-", "?"))) %>%
  dplyr::mutate(confidence = tolower(confidence)) %>%
  dplyr::mutate(confidence = factor(confidence, levels = c("weak", "strong", "confirmed")))

all_tfgnw_by_evidence <- all_tfgnw %>%
  tidyr::separate_rows(evidence, sep = ",") %>%
  dplyr::mutate(evidence = trimws(gsub("\\[|\\]", "", evidence))) %>% 
  dplyr::mutate(evidence_code = "",
                evidence_level = "",
                evidence_name = "") %>%
  dplyr::rowwise() %>%
  dplyr::mutate(evidence_code = ifelse(grepl("\\|", evidence), stringr::str_split(evidence, "\\|")[[1]][1], evidence),
                evidence_level = ifelse(grepl("\\|", evidence), stringr::str_split(evidence, "\\|")[[1]][2], NA),
                evidence_name = ifelse(grepl("\\|", evidence), stringr::str_split(evidence, "\\|")[[1]][3], NA)
                )


```

**NB: additional TAB characters at the end of each line cause parsing issues**

## Releases

Comparison of the network_tf_gene.txt file between the last releases.

| Release version     | Date           |
|---------------------|----------------|
| 10.6 (NA)                | 2019 July      |
| 10.6.3              | -              |
| 10.7                | 2020 April     |
| 10.8                | 2020 October   |
| 10.9                | 2021 April     |
| 10.10 (NA)               | 2022 February  |
| 11.0                | 2022 August    |
| 11.0.1 (not public) | 2022 September |

```{r total-tfgnw, fig.height=4, fig.width=6}
tfgnw_summary <- all_tfgnw %>%
  dplyr::group_by(version) %>%
  dplyr::summarise(total = n()) %>%
  dplyr::arrange(version)

tfgnw_num <- simple_bar(tfgnw_summary, "version", "total") +
  scale_fill_viridis(discrete = T) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "Release version", y = "Number of TF-gene entries", title = "")

tfgnw_num

DT::datatable(tfgnw_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```



## TF-gene pairs 

```{r pairs-shared}
pairs <- list()
for (v in tfgnw_versions) {
	pairs[[v]] <- unique( (get(paste0("tfgnw_set_", v)))$pairs)
}
UpSetR::upset(fromList(pairs), sets = tfgnw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              # queries = list(
              #                list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
              #                list(query = intersects, params = list("v10.7", "v10.8"), color = "red", active = T)
              #                )
              )
```

```{r pairs-dupli}
coords_dupli <- all_tfgnw %>%
  dplyr::group_by(version, pairs) %>%
  dplyr::summarise(occurrences = n()) %>%
	  group_by(version, occurrences) %>% 
	  summarise(pairs_number = n())%>%
  dplyr::mutate(occurrences = factor(occurrences))

###
dodge <- ggplot(coords_dupli, aes(fill = occurrences, y = pairs_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "", y = "Number of unique TF-gene pairs", title = "TF-gene pairs duplication in network_tf_gene.txt across versions")

dodge2 <- ggplot(coords_dupli %>% dplyr::filter(!occurrences %in% c("1", "2", "3", "4")), aes(fill = occurrences, y = pairs_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14),
        legend.position = "none") +
  labs(x = "", y = "Number of unique TF-gene pairs", title = "...minimum 5 copies")

dodge / dodge2 

```

### Which pairs are most duplicated?

```{r which-dupli-pairs}
## pairs that have at least 10 entries in a given version
pairs_dupli_max <- all_tfgnw %>%
  dplyr::group_by(version, pairs) %>%
  dplyr::summarise(occurrences = n()) %>%
  dplyr::filter(occurrences >=10) %>%
  dplyr::arrange(desc(occurrences)) %>%
  pivot_wider(names_from = version,
              values_from = c(occurrences))

DT::datatable(pairs_dupli_max, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))
```







## TFs

```{r tfs-shared-tfgnw}
tf_names <- list()
for (v in tfgnw_versions) {
	tf_names[[v]] <- unique( (get(paste0("tfgnw_set_", v)))$TF_name)
}
UpSetR::upset(fromList(tf_names), sets = tfgnw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TF names",
              # queries = list(list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )
```



## Genes

```{r genes-shared-tfgnw}
gene_names <- list()
for (v in tfgnw_versions) {
	gene_names[[v]] <- unique( (get(paste0("tfgnw_set_", v)))$gene_name)
}
UpSetR::upset(fromList(gene_names), sets = tfgnw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TF names",
              # queries = list(list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )

```









## Effect

```{r tfgnw-effect, fig.width=10}
tfgnw_effect_long <- all_tfgnw %>% 
  group_by(version, effect) %>% 
  summarise(value = n()) 

dodge <- ggplot(tfgnw_effect_long, aes(fill = effect, y = value, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of tfgnw", title = "")

stack <- ggplot(tfgnw_effect_long, aes(fill = effect, y = value, x = version)) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of tfgnw", title = "")

line <-  ggplot(tfgnw_effect_long, aes(group = effect, y = value, x = version)) + 
  geom_line(aes(color = effect)) +
  geom_point(size = 2, aes(color = effect)) +
  scale_color_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "Release version", y = "Number of tfgnw", title = "")

## ggplotly to make it interactive
# fig0 <- ggplotly(tfgnw_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig1, fig2, fig3, nrows=3)
```


```{r tfgnw-effect-summary}
effect_summary <- all_tfgnw %>% 
  group_by(version, effect) %>% 
  summarise(value = n())  %>%
  data.frame() %>%
  pivot_wider(names_from = version, values_from = c(value)) %>%
   arrange(effect)

DT::datatable(effect_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```

## Evidence 

```{r tfgnw-evidence}
tfgnw_evidence_long <- all_tfgnw_by_evidence %>% 
  group_by(version, evidence_code) %>% 
  summarise(value = n(), evidence_name = concat_uniq(evidence_name)) ## ojo que solo la 11.0.1 tiene evidence name

evidence_palette <- random_palette(length(unique(all_tfgnw_by_evidence$evidence_code)))

##----
dodge <- ggplot(tfgnw_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
    scale_fill_manual(values = evidence_palette, drop = F, na.value = "gray") +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of tfgnws", title = "")

stack <- ggplot(tfgnw_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) + 
  geom_bar(position = "stack", stat = "identity") +
    scale_fill_manual(values = evidence_palette, drop = F, na.value = "gray") +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of evidence", title = "")

line <-  ggplot(tfgnw_evidence_long, aes(group = evidence_code, y = value, x = version)) + 
  geom_line(aes(color = evidence_code)) +
  scale_color_manual(values = evidence_palette, drop = F, na.value = "gray") +
  geom_point(size = 2, aes(color = evidence_code)) +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "Release version", y = "Number of tfgnw", title = "")

fig0 <- ggplotly(tfgnw_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig0, fig1, fig2, fig3, nrows=4)

```

```{r tfgnw-evidence-table}

tfgnw_evidence_table <- all_tfgnw_by_evidence %>% 
  group_by(evidence_code) %>% 
  summarise(value = n(), evidence_name = concat_uniq(evidence_name), version = concat_uniq(version)) ## ojo que solo la 11.0.1 tiene evidence name

DT::datatable(tfgnw_evidence_table, rownames= FALSE, options = list(searching = TRUE, lengthChange = FALSE, pageLength = 10))

## to do remove empty string from evidence table
```

```{r tfgnw-evidence-upset}

tfgnw_evidence_shared <- list()
for (v in tfgnw_versions) {
	tfgnw_evidence_shared[[v]] <- unique((all_tfgnw_by_evidence %>% dplyr::filter(version == v))$evidence_code)
}

UpSetR::upset(fromList(tfgnw_evidence_shared), sets = tfgnw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              # queries = list(list(query = intersects, params = list("v10.7"), color = "red", active = T),
              #                list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T))
              )

## Revise congruency between table and upset plot (table has CE listed as only present in 10.8, shjould have 10.7 too)
```


## Confidence 

```{r tfgnw-confidence, fig.width=10}
tfgnw_confidence_long <- all_tfgnw %>% 
  group_by(version, confidence) %>% 
  summarise(value = n()) 

dodge <- ggplot(tfgnw_confidence_long, aes(fill = confidence, y = value, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of tfgnw", title = "")

stack <- ggplot(tfgnw_confidence_long, aes(fill = confidence, y = value, x = version)) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of tfgnw", title = "")

line <-  ggplot(tfgnw_confidence_long, aes(group = confidence, y = value, x = version)) + 
  geom_line(aes(color = confidence)) +
  geom_point(size = 2, aes(color = confidence)) +
  scale_color_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "Release version", y = "Number of tfgnw", title = "")

## ggplotly to make it interactive
# fig0 <- ggplotly(tfgnw_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig1, fig2, fig3, nrows=3)
```


```{r confidence-summary-tfgnw}
confidence_summary <- all_tfgnw %>% 
  group_by(version, confidence) %>% 
  summarise(value = n())  %>%
  mutate(confidence = ifelse(is.na(confidence), "null", as.character(confidence))) %>%
  data.frame() %>%
  pivot_wider(names_from = version, values_from = c(value)) %>%
  mutate(across(starts_with('v'), ~replace_na(.,0))) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~"total"))) %>%
   mutate(confidence = factor(confidence, levels = c("weak", "strong", "confirmed", "null", "total"))) %>%
   arrange(confidence)

DT::datatable(confidence_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```


# network_tf_tu.txt  {.tabset}

```{r network-tf-tu-data1}
dir_versions <- c("10.6.3", "10.7", "10.8", "10.9", "11.0", "11.0.1")
tftunw_sets <- list()
tftunw_versions <- c()

for(v in dir_versions){
  version_tag <- paste0("v", v)
  set <- read.delim(paste0(dir_releases, "/", v, "/network_tf_tu.tsv"), 
                    comment.char = "#", header = T, stringsAsFactors = F, na.strings = c("", "NA")) %>% 
    dplyr::mutate(effect = ifelse(effect == "repressor", "-", ifelse(effect == "activator", "+", ifelse(effect == "unknown", "?", effect)))) %>%
    dplyr::mutate(version = version_tag) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(evidence = ifelse("evidence_function" %in% colnames(.), concat_uniq2(evidence, evidence_function), evidence)) %>%
    dplyr::mutate(pairs = paste0(TF_name, "_", TU_name)) 

  
  assign(paste0("tftunw_set_", version_tag), set)
  tftunw_sets[[version_tag]] <- set
  tftunw_versions <- c(tftunw_versions, version_tag)
  
}
all_tftunw <- bind_rows(tftunw_sets) %>%
  dplyr::mutate(version = factor(version, levels =  tftunw_versions)) %>%
  dplyr::mutate(effect = factor(effect, levels =  c("+", "-", "?"))) %>%
  dplyr::mutate(confidence = tolower(confidence)) %>%
  dplyr::mutate(confidence = factor(confidence, levels = c("weak", "strong", "confirmed")))

all_tftunw_by_evidence <- all_tftunw %>%
  tidyr::separate_rows(evidence, sep = ",") %>%
  dplyr::mutate(evidence = trimws(gsub("\\[|\\]", "", evidence))) %>% 
  dplyr::mutate(evidence_code = "",
                evidence_level = "",
                evidence_name = "") %>%
  dplyr::rowwise() %>%
  dplyr::mutate(evidence_code = ifelse(grepl("\\|", evidence), stringr::str_split(evidence, "\\|")[[1]][1], evidence),
                evidence_level = ifelse(grepl("\\|", evidence), stringr::str_split(evidence, "\\|")[[1]][2], NA),
                evidence_name = ifelse(grepl("\\|", evidence), stringr::str_split(evidence, "\\|")[[1]][3], NA)
                )


```

**NB: additional TAB characters at the end of each line cause parsing issues**

## Releases

Comparison of the network_tf_gene.txt file between the last releases.

| Release version     | Date           |
|---------------------|----------------|
| 10.6 (NA)                | 2019 July      |
| 10.6.3              | -              |
| 10.7                | 2020 April     |
| 10.8                | 2020 October   |
| 10.9                | 2021 April     |
| 10.10 (NA)               | 2022 February  |
| 11.0                | 2022 August    |
| 11.0.1 (not public) | 2022 September |

```{r total-tftunw, fig.height=4, fig.width=6}
tftunw_summary <- all_tftunw %>%
  dplyr::group_by(version) %>%
  dplyr::summarise(total = n()) %>%
  dplyr::arrange(version)

tftunw_num <- simple_bar(tftunw_summary, "version", "total") +
  scale_fill_viridis(discrete = T) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "Release version", y = "Number of TF-gene entries", title = "")

tftunw_num

DT::datatable(tftunw_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```



## TF-gene pairs 

```{r tftu-pairs-shared}
pairs <- list()
for (v in tftunw_versions) {
	pairs[[v]] <- unique( (get(paste0("tftunw_set_", v)))$pairs)
}
UpSetR::upset(fromList(pairs), sets = tftunw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              # queries = list(
              #                list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T),
              #                list(query = intersects, params = list("v10.7", "v10.8"), color = "red", active = T)
              #                )
              )
```

```{r tftu-pairs-dupli}
coords_dupli <- all_tftunw %>%
  dplyr::group_by(version, pairs) %>%
  dplyr::summarise(occurrences = n()) %>%
	  group_by(version, occurrences) %>% 
	  summarise(pairs_number = n())%>%
  dplyr::mutate(occurrences = factor(occurrences))

###
dodge <- ggplot(coords_dupli, aes(fill = occurrences, y = pairs_number, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) +
  labs(x = "", y = "Number of unique TF-gene pairs", title = "TF-gene pairs duplication in network_tf_gene.txt across versions")


dodge 

```







## TFs

```{r tfs-shared-tftunw}
tf_names <- list()
for (v in tftunw_versions) {
	tf_names[[v]] <- unique( (get(paste0("tftunw_set_", v)))$TF_name)
}
UpSetR::upset(fromList(tf_names), sets = tftunw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TF names",
              # queries = list(list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )
```



## Genes

```{r genes-shared-tftunw}
TU_names <- list()
for (v in tftunw_versions) {
	TU_names[[v]] <- unique( (get(paste0("tftunw_set_", v)))$TU_name)
}
UpSetR::upset(fromList(TU_names), sets = tftunw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              sets.x.label  = "Number of unique TU names",
              # queries = list(list(query = intersects, params = list("v10.7", "v10.8", "v10.9"), color = "red", active = T))
              )

```



## Effect

```{r tftunw-effect, fig.width=10}
tftunw_effect_long <- all_tftunw %>% 
  group_by(version, effect) %>% 
  summarise(value = n()) 

dodge <- ggplot(tftunw_effect_long, aes(fill = effect, y = value, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of tftunw", title = "")

stack <- ggplot(tftunw_effect_long, aes(fill = effect, y = value, x = version)) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of tftunw", title = "")

line <-  ggplot(tftunw_effect_long, aes(group = effect, y = value, x = version)) + 
  geom_line(aes(color = effect)) +
  geom_point(size = 2, aes(color = effect)) +
  scale_color_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "Release version", y = "Number of tftunw", title = "")

## ggplotly to make it interactive
# fig0 <- ggplotly(tftunw_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig1, fig2, fig3, nrows=3)
```


```{r tftunw-effect-summary}
effect_summary <- all_tftunw %>% 
  group_by(version, effect) %>% 
  summarise(value = n())  %>%
  data.frame() %>%
  pivot_wider(names_from = version, values_from = c(value)) %>%
   arrange(effect)

DT::datatable(effect_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```

## Evidence 

```{r tftunw-evidence}
tftunw_evidence_long <- all_tftunw_by_evidence %>% 
  group_by(version, evidence_code) %>% 
  summarise(value = n(), evidence_name = concat_uniq(evidence_name)) ## ojo que solo la 11.0.1 tiene evidence name

evidence_palette <- random_palette(length(unique(all_tftunw_by_evidence$evidence_code)))

##----
dodge <- ggplot(tftunw_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
    scale_fill_manual(values = evidence_palette, drop = F, na.value = "gray") +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of tftunws", title = "")

stack <- ggplot(tftunw_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) + 
  geom_bar(position = "stack", stat = "identity") +
    scale_fill_manual(values = evidence_palette, drop = F, na.value = "gray") +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of evidence", title = "")

line <-  ggplot(tftunw_evidence_long, aes(group = evidence_code, y = value, x = version)) + 
  geom_line(aes(color = evidence_code)) +
  scale_color_manual(values = evidence_palette, drop = F, na.value = "gray") +
  geom_point(size = 2, aes(color = evidence_code)) +
  # scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "Release version", y = "Number of tftunw", title = "")

fig0 <- ggplotly(tftunw_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig0, fig1, fig2, fig3, nrows=4)

```

```{r tftunw-evidence-table}

tftunw_evidence_table <- all_tftunw_by_evidence %>% 
  group_by(evidence_code) %>% 
  summarise(value = n(), evidence_name = concat_uniq(evidence_name), version = concat_uniq(version)) ## ojo que solo la 11.0.1 tiene evidence name

DT::datatable(tftunw_evidence_table, rownames= FALSE, options = list(searching = TRUE, lengthChange = FALSE, pageLength = 10))

## to do remove empty string from evidence table
```

```{r tftunw-evidence-upset}

tftunw_evidence_shared <- list()
for (v in tftunw_versions) {
	tftunw_evidence_shared[[v]] <- unique((all_tftunw_by_evidence %>% dplyr::filter(version == v))$evidence_code)
}

UpSetR::upset(fromList(tftunw_evidence_shared), sets = tftunw_versions, order.by = "freq", keep.order = T,
              text.scale = c(2,2,2,2,2,2),
              # queries = list(list(query = intersects, params = list("v10.7"), color = "red", active = T),
              #                list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T))
              )

## Revise congruency between table and upset plot (table has CE listed as only present in 10.8, shjould have 10.7 too)
```


## Confidence 

```{r tftunw-confidence, fig.width=10}
tftunw_confidence_long <- all_tftunw %>% 
  group_by(version, confidence) %>% 
  summarise(value = n()) 

dodge <- ggplot(tftunw_confidence_long, aes(fill = confidence, y = value, x = version)) + 
  geom_bar(position = position_dodge(preserve = "single"), stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "", y = "Number of tftunw", title = "")

stack <- ggplot(tftunw_confidence_long, aes(fill = confidence, y = value, x = version)) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") +
  labs(x = "", y = "Number of tftunw", title = "")

line <-  ggplot(tftunw_confidence_long, aes(group = confidence, y = value, x = version)) + 
  geom_line(aes(color = confidence)) +
  geom_point(size = 2, aes(color = confidence)) +
  scale_color_viridis(discrete = T, na.value = "gray", drop = F) +
  theme_minimal() +
  theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") +
  labs(x = "Release version", y = "Number of tftunw", title = "")

## ggplotly to make it interactive
# fig0 <- ggplotly(tftunw_num)
fig1 <- ggplotly(dodge)
fig2 <- ggplotly(stack)
fig3 <- ggplotly(line)

subplot(fig1, fig2, fig3, nrows=3)
```


```{r confidence-summary-tftunw}
confidence_summary <- all_tftunw %>% 
  group_by(version, confidence) %>% 
  summarise(value = n())  %>%
  mutate(confidence = ifelse(is.na(confidence), "null", as.character(confidence))) %>%
  data.frame() %>%
  pivot_wider(names_from = version, values_from = c(value)) %>%
  mutate(across(starts_with('v'), ~replace_na(.,0))) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~"total"))) %>%
   mutate(confidence = factor(confidence, levels = c("weak", "strong", "confirmed", "null", "total"))) %>%
   arrange(confidence)

DT::datatable(confidence_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10))

```


<!-- <!-- NEWWW --> -->
<!-- ## Evidence in network TF-gene -->

<!-- **NB: evidence is formatted in different ways between versions of downloadable file, which can cause parsing issues** -->

<!-- ```{r network-evidence1, fig.width=10} -->
<!-- # tf_gene_evidence <- bind_rows(network_set_10.6.3, network_set_10.7, network_set_10.8, network_set_10.9, network_set_11.0) %>% -->
<!-- #   tidyr::separate_rows(evidence, sep = ",") %>% -->
<!-- #   dplyr::mutate(evidence_code = gsub("\\[|\\]", "", evidence))  -->
<!-- #  -->
<!-- # last <- network_set_11.0.1 %>% -->
<!-- #   dplyr::mutate(evidence_function = gsub("\\[\\]", "\\[\\|\\|\\]", evidence_function)) %>% -->
<!-- #   dplyr::mutate(evidence = gsub("\\[\\]", "\\[\\|\\|\\]", evidence)) %>% -->
<!-- #   dplyr::rowwise() %>% -->
<!-- #   dplyr::mutate(evidence = concat_uniq(evidence, evidence_function)) %>% -->
<!-- #   tidyr::separate_rows(evidence, sep = ",") %>% -->
<!-- #   dplyr::mutate(evidence = gsub("\\[|\\]", "", evidence)) %>% -->
<!-- #   tidyr::separate(evidence, c("evidence_code", "evidence_level", "evidence_name"), sep = "\\|")  -->
<!-- #   # dplyr::mutate(fevidence = gsub("\\[|\\]", "", evidence_function)) %>% -->
<!-- #   # tidyr::separate(fevidence, c("fevidence_code", "fevidence_level", "fevidence_name"), sep = "\\|") -->
<!-- #  -->
<!-- # tf_gene_evidence <- bind_rows(tf_gene_evidence, last) -->
<!-- # tf_gene_evidence$version <- factor(tf_gene_evidence$version, levels = paste0("v", tfgnw_versions)) -->


<!-- tf_gene_evidence <- bind_rows(network_set_10.7, network_set_10.8, network_set_10.9, network_set_11.0) %>% -->
<!--   tidyr::separate_rows(evidence, sep = ",") %>% -->
<!--   dplyr::mutate(evidence_code = gsub("\\[|\\]", "", evidence))  -->

<!-- last <- network_set_11.0.1 %>% -->
<!--   dplyr::mutate(evidence_function = gsub("\\[\\]", "\\[\\|\\|\\]", evidence_function)) %>% -->
<!--   dplyr::mutate(evidence = gsub("\\[\\]", "\\[\\|\\|\\]", evidence)) %>% -->
<!--   dplyr::rowwise() %>% -->
<!--   dplyr::mutate(evidence = paste0(evidence, ",", evidence_function)) %>% -->
<!--   tidyr::separate_rows(evidence, sep = ",") %>% -->
<!--   dplyr::mutate(evidence = gsub("\\[|\\]", "", evidence)) %>% -->
<!--   tidyr::separate(evidence, c("evidence_code", "evidence_level", "evidence_name"), sep = "\\|")  -->
<!--   # dplyr::mutate(fevidence = gsub("\\[|\\]", "", evidence_function)) %>% -->
<!--   # tidyr::separate(fevidence, c("fevidence_code", "fevidence_level", "fevidence_name"), sep = "\\|") -->

<!-- tf_gene_evidence <- bind_rows(tf_gene_evidence, last)%>% -->
<!--   dplyr::mutate(evidence_code = trimws(evidence_code))  -->

<!-- tf_gene_evidence$version <- factor(tf_gene_evidence$version, levels = paste0("v", tfgnw_versions)) -->

<!-- # -->
<!-- ## -->
<!-- tf_gene_evidence_long <- tf_gene_evidence %>%  -->
<!--   group_by(version, evidence_code) %>%  -->
<!--   summarise(value = n())  -->

<!-- dodge <- ggplot(tf_gene_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) +  -->
<!--   geom_bar(position = position_dodge(preserve = "single"), stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") + -->
<!--   labs(x = "", y = "Number of entries", title = "") -->

<!-- stack <- ggplot(tf_gene_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) +  -->
<!--   geom_bar(position = "stack", stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "", y = "Number of evidence", title = "") -->

<!-- line <-  ggplot(tf_gene_evidence_long, aes(y = value, x = version, group = evidence_code)) +  -->
<!--   geom_line(aes(color = evidence_code)) + -->
<!--   geom_point(size = 2, aes(color = evidence_code)) + -->
<!--   scale_color_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "Release version", y = "Number of entries", title = "") -->

<!-- fig0 <- ggplotly(tf_gene_num) -->
<!-- fig1<-ggplotly(dodge) -->
<!-- fig2<-ggplotly(stack) -->
<!-- fig3<-ggplotly(line) -->

<!-- subplot(fig0, fig1, fig2, fig3, nrows=4, shareY = TRUE) -->



<!-- ``` -->


<!-- ## Confidence  -->

<!-- **NB: confidence is now written in the downloadable file in all caps, which can cause mapping issues** -->


<!-- ```{r tfgenebs-confidence, fig.width=10} -->
<!-- confidence_nw_all_versions <- list() -->
<!-- for(v in tfgnw_versions){ -->
<!--   confidence_nw_all_versions[[v]] <- get(paste0("network_set_", v)) %>%  -->
<!--     group_by(version, confidence) %>%  -->
<!--     summarise(value = n()) -->
<!-- } -->
<!-- confidence_nw_all_versions_df <- data.table::rbindlist(confidence_nw_all_versions) %>% -->
<!--   dplyr::mutate(confidence = tolower(confidence))  -->
<!-- confidence_nw_all_versions_df$confidence <- factor(confidence_nw_all_versions_df$confidence, levels = c("weak", "strong", "confirmed")) -->
<!-- confidence_nw_all_versions_df$version <- factor(confidence_nw_all_versions_df$version, levels = paste0("v", tfgnw_versions)) -->

<!-- ## -->
<!-- tf_gene_confidence_long <- confidence_nw_all_versions_df -->

<!-- dodge <- ggplot(tf_gene_confidence_long, aes(fill = confidence, y = value, x = version)) +  -->
<!--   geom_bar(position = position_dodge(preserve = "single"), stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") + -->
<!--   labs(x = "", y = "Number of entries", title = "") -->

<!-- stack <- ggplot(tf_gene_confidence_long, aes(fill = confidence, y = value, x = version)) +  -->
<!--   geom_bar(position = "stack", stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "", y = "Number of TFBS", title = "") -->

<!-- line <-  ggplot(tf_gene_confidence_long, aes(group = confidence, y = value, x = version)) +  -->
<!--   geom_line(aes(color = confidence)) + -->
<!--   geom_point(size = 2, aes(color = confidence)) + -->
<!--   scale_color_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "Release version", y = "Number of entries", title = "") -->

<!-- fig0 <- ggplotly(tf_gene_num) -->
<!-- fig1<-ggplotly(dodge) -->
<!-- fig2<-ggplotly(stack) -->
<!-- fig3<-ggplotly(line) -->

<!-- subplot(fig0, fig1, fig2, fig3, nrows=4, shareY = T) -->
<!-- ``` -->


<!-- ```{r evidence-level-tfbs-3tab} -->
<!-- confidence_nw_summary <- confidence_nw_all_versions_df %>% -->
<!--   arrange(confidence) %>% -->
<!--   mutate(confidence = ifelse(is.na(confidence), "null", as.character(confidence))) %>% -->
<!--   # mutate(value = ifelse(is.na(value), 0, value)) %>% -->
<!--   data.frame() %>% -->
<!--   pivot_wider(names_from = version, values_from = c(value)) %>% -->
<!--   mutate(across(starts_with('v'), ~replace_na(.,0))) %>% -->
<!--   bind_rows(summarise(., -->
<!--                       across(where(is.numeric), sum), -->
<!--                       across(where(is.character), ~"total"))) -->

<!-- DT::datatable(confidence_nw_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10)) -->

<!-- ``` -->



<!-- ## Mapping -->

<!-- ```{r tf-gene-mapping, eval = F} -->
<!-- all_tf_gene <- network_set_10.6.3 %>% -->
<!--   dplyr::full_join(network_set_10.7 %>% dplyr::select(TF_name, gene_name, effect, evidence, confidence),  -->
<!--                    by = c("TF_name", "gene_name", "effect"), suffix = c("_10.6.3", "_10.7")) %>% -->
<!--   dplyr::full_join(network_set_10.8 %>% dplyr::select(TF_name, gene_name, effect, evidence, confidence),  -->
<!--                    by = c("TF_name", "gene_name", "effect"), suffix = c("_10.7", "_10.8")) %>% -->
<!--   dplyr::full_join(network_set_10.9 %>% dplyr::select(TF_name, gene_name, effect, evidence, confidence),  -->
<!--                    by = c("TF_name", "gene_name", "effect"), suffix = c("_10.8", "_10.9")) %>% -->
<!--   dplyr::full_join(network_set_11.0 %>% dplyr::select(TF_name, gene_name, effect, evidence, confidence),  -->
<!--                    by = c("TF_name", "gene_name", "effect"), suffix = c("_10.9", "_11.0")) %>% -->
<!--   dplyr::full_join(network_set_11.0.1 %>% dplyr::select(TF_name, gene_name, effect, evidence, evidence_function, confidence),  -->
<!--                    by = c("TF_name", "gene_name", "effect"), suffix = c("_11.0", "_11.0.1")) %>% -->
<!--   dplyr::arrange(TF_name, gene_name) -->
<!--   # distinct() -->
<!--   # dplyr::rename(confidence_11.0.2 = confidence, evidence_11.0.2 = evidence) -->

<!-- write.table(all_tf_gene, file = "all_tf_gene.tsv", quote = F, row.names = F, col.names = T, sep = "\t") -->
<!-- ``` -->

<!-- # network_tf_tu.txt {.tabset} -->

<!-- ## Data -->

<!-- ```{r network-tf-gene-data2} -->
<!-- tfgnw_versions <- setdiff(dir_versions, c("10.10", "11.0.2")) -->
<!-- for(v in tfgnw_versions){ -->
<!--   assign(paste0("network_tu_set_", v), read.delim(paste0(dir_releases, "/", v, "/network_tf_tu.tsv"), comment.char = "#", header = T, stringsAsFactors = F, na.strings = "")%>% dplyr::mutate(version = paste0("v", v)))  -->
<!-- } -->
<!-- ``` -->

<!-- **NB: additional TAB characters at the end of each line cause parsing issues** -->

<!-- ```{r total-tf-tu, fig.height=5, fig.width=6} -->
<!-- tf_tu_summary <- list() -->
<!-- for(v in tfgnw_versions){ -->
<!-- 	tf_tu_summary[[paste0("v", v)]] <- data.frame(version = paste0("v", v), count = nrow(get(paste0("network_tu_set_", v)))) -->
<!-- } -->
<!-- tf_tu_summary_df <- data.table::rbindlist(tf_tu_summary) -->
<!-- tf_gene_summary_df$version <- factor(tf_tu_summary_df$version, levels = paste0("v", tfgnw_versions)) -->


<!-- DT::datatable(tf_tu_summary_df, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10)) -->

<!-- tf_tu_num <- simple_bar(tf_tu_summary_df, "version", "count") + -->
<!--   scale_fill_viridis(discrete = T) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) + -->
<!--   labs(x = "Release version", y = "Number of entries", title = "") -->

<!-- tf_tu_num -->
<!-- ``` -->

<!-- ## TF-TU pairs  -->

<!-- ```{r tf-tu-ids-upset, fig.height=8} -->
<!-- tf_tu_pairs <- list() -->
<!-- for (v in tfgnw_versions) { -->
<!--   pairs <- get(paste0("network_tu_set_", v)) %>% -->
<!--     rowwise() %>% -->
<!--     mutate(TF_TU = paste0(TF_name, "_", TU_name)) -->
<!-- 	tf_tu_pairs[[paste0("v", v)]] <- unique(pairs$TF_TU) -->
<!-- } -->
<!-- UpSetR::upset(fromList(tf_tu_pairs), sets = paste0("v", tfgnw_versions), order.by = "freq", keep.order = T, -->
<!--               text.scale = c(2,2,2,2,2,2), -->
<!--               # queries = list(list(query = intersects, params = list("v10.6", "v10.6.3", "v10.7"), color = "red", active = T), -->
<!--               #                list(query = intersects, params = list("v10.9", "v10.10", "v11.0", "v11.0.1", "v11.0.2"), color = "blue", active = T)) -->
<!--               ) -->
<!-- ``` -->

<!-- ### Duplicate TF-TU pairs  -->

<!-- ```{r tf-tu-dupli} -->
<!-- pairs_tu_ids_dupli <- list() -->
<!-- for (v in tfgnw_versions) { -->
<!-- 	pairs_tu_ids_dupli[[paste0("v", v)]] <- get(paste0("network_tu_set_", v)) %>%  -->
<!--     rowwise() %>% -->
<!--     mutate(TF_TU = paste0(TF_name, "_", TU_name)) %>% -->
<!-- 	  group_by(TF_TU) %>%  -->
<!-- 	  summarise(occurrences = n()) %>%  -->
<!-- 	  group_by(occurrences) %>%  -->
<!-- 	  summarise(pairs_number = n()) %>% -->
<!-- 	  mutate(version = paste0("v", v)) -->
<!-- } -->

<!-- pairs_tu_ids_dupli_df <- data.table::rbindlist(pairs_tu_ids_dupli) %>% -->
<!--   dplyr::mutate(occurrences = factor(occurrences)) -->

<!-- pairs_tu_ids_dupli_df$version <- factor(pairs_tu_ids_dupli_df$version, levels = paste0("v", tfgnw_versions)) -->

<!-- ### -->
<!-- dodge <- ggplot(pairs_tu_ids_dupli_df, aes(fill = occurrences, y = pairs_number, x = version)) +  -->
<!--   geom_bar(position = position_dodge(preserve = "single"), stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14)) + -->
<!--   labs(x = "", y = "Number of pairs", title = "TF-TU pairs duplication in network_tf_gene.txt across versions") -->

<!-- dodge  -->
<!-- ``` -->

<!-- ## Evidence in network TF-TU -->

<!-- **NB: evidence is formatted in different ways between versions of downloadable file, which can cause parsing issues** -->

<!-- ```{r network-evidence2, fig.width=10} -->
<!-- tf_tu_evidence <- bind_rows(network_tu_set_10.7, network_tu_set_10.8, network_tu_set_10.9, network_tu_set_11.0) %>% -->
<!--   tidyr::separate_rows(evidence, sep = ",") %>% -->
<!--   dplyr::mutate(evidence_code = gsub("\\[|\\]", "", evidence))  -->

<!-- last <- network_tu_set_11.0.1 %>% -->
<!--   dplyr::mutate(evidence_function = gsub("\\[\\]", "\\[\\|\\|\\]", evidence_function)) %>% -->
<!--   dplyr::mutate(evidence = gsub("\\[\\]", "\\[\\|\\|\\]", evidence)) %>% -->
<!--   dplyr::rowwise() %>% -->
<!--   dplyr::mutate(evidence = paste0(evidence, ",", evidence_function)) %>% -->
<!--   tidyr::separate_rows(evidence, sep = ",") %>% -->
<!--   dplyr::mutate(evidence = gsub("\\[|\\]", "", evidence)) %>% -->
<!--   tidyr::separate(evidence, c("evidence_code", "evidence_level", "evidence_name"), sep = "\\|")  -->
<!--   # dplyr::mutate(fevidence = gsub("\\[|\\]", "", evidence_function)) %>% -->
<!--   # tidyr::separate(fevidence, c("fevidence_code", "fevidence_level", "fevidence_name"), sep = "\\|") -->

<!-- tf_tu_evidence <- bind_rows(tf_tu_evidence, last)%>% -->
<!--   dplyr::mutate(evidence_code = trimws(evidence_code))  -->

<!-- tf_tu_evidence$version <- factor(tf_tu_evidence$version, levels = paste0("v", tfgnw_versions)) -->

<!-- ## -->
<!-- tf_tu_evidence_long <- tf_tu_evidence %>%  -->
<!--   group_by(version, evidence_code) %>%  -->
<!--   summarise(value = n())  -->

<!-- dodge <- ggplot(tf_tu_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) +  -->
<!--   geom_bar(position = position_dodge(preserve = "single"), stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") + -->
<!--   labs(x = "", y = "Number of entries", title = "") -->

<!-- stack <- ggplot(tf_tu_evidence_long, aes(fill = evidence_code, y = value, x = version, group = evidence_code)) +  -->
<!--   geom_bar(position = "stack", stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "", y = "Number of evidence", title = "") -->

<!-- line <-  ggplot(tf_tu_evidence_long, aes(y = value, x = version, group = evidence_code)) +  -->
<!--   geom_line(aes(color = evidence_code)) + -->
<!--   geom_point(size = 2, aes(color = evidence_code)) + -->
<!--   scale_color_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "Release version", y = "Number of entries", title = "") -->

<!-- fig0 <- ggplotly(tf_tu_num) -->
<!-- fig1<-ggplotly(dodge) -->
<!-- fig2<-ggplotly(stack) -->
<!-- fig3<-ggplotly(line) -->

<!-- subplot(fig0, fig1, fig2, fig3, nrows=4, shareY = TRUE) -->



<!-- ``` -->


<!-- ## Confidence  -->

<!-- **NB: confidence is now written in the downloadable file in all caps, which can cause mapping issues** -->

<!-- #### OJO confidence evolution is weired compared to tf-gene and TFBSseeet -->

<!-- ```{r tfnw-confidence2, fig.width=10} -->
<!-- confidence_nw_all_versions <- list() -->
<!-- for(v in tfgnw_versions){ -->
<!--   confidence_nw_all_versions[[v]] <- get(paste0("network_set_", v)) %>%  -->
<!--     group_by(version, confidence) %>%  -->
<!--     summarise(value = n()) -->
<!-- } -->
<!-- confidence_nw_all_versions_df <- data.table::rbindlist(confidence_nw_all_versions) %>% -->
<!--   dplyr::mutate(confidence = tolower(confidence))  -->
<!-- confidence_nw_all_versions_df$confidence <- factor(confidence_nw_all_versions_df$confidence, levels = c("weak", "strong", "confirmed")) -->
<!-- confidence_nw_all_versions_df$version <- factor(confidence_nw_all_versions_df$version, levels = paste0("v", tfgnw_versions)) -->

<!-- ## -->
<!-- tf_gene_confidence_long <- confidence_nw_all_versions_df -->

<!-- dodge <- ggplot(tf_gene_confidence_long, aes(fill = confidence, y = value, x = version)) +  -->
<!--   geom_bar(position = position_dodge(preserve = "single"), stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "right") + -->
<!--   labs(x = "", y = "Number of entries", title = "") -->

<!-- stack <- ggplot(tf_gene_confidence_long, aes(fill = confidence, y = value, x = version)) +  -->
<!--   geom_bar(position = "stack", stat = "identity") + -->
<!--   scale_fill_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "", y = "Number of TFBS", title = "") -->

<!-- line <-  ggplot(tf_gene_confidence_long, aes(group = confidence, y = value, x = version)) +  -->
<!--   geom_line(aes(color = confidence)) + -->
<!--   geom_point(size = 2, aes(color = confidence)) + -->
<!--   scale_color_viridis(discrete = T, na.value = "gray", drop = F) + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text = element_text(size = 14), axis.title.y = element_text(size = 14), title = element_text(size = 14), legend.position = "none") + -->
<!--   labs(x = "Release version", y = "Number of entries", title = "") -->

<!-- fig0 <- ggplotly(tf_gene_num) -->
<!-- fig1<-ggplotly(dodge) -->
<!-- fig2<-ggplotly(stack) -->
<!-- fig3<-ggplotly(line) -->

<!-- subplot(fig0, fig1, fig2, fig3, nrows=4, shareY = T) -->
<!-- ``` -->


<!-- ```{r evidence-level-tfbs-tab1} -->
<!-- confidence_nw_summary <- confidence_nw_all_versions_df %>% -->
<!--   arrange(confidence) %>% -->
<!--   mutate(confidence = ifelse(is.na(confidence), "null", as.character(confidence))) %>% -->
<!--   # mutate(value = ifelse(is.na(value), 0, value)) %>% -->
<!--   data.frame() %>% -->
<!--   pivot_wider(names_from = version, values_from = c(value)) %>% -->
<!--   mutate(across(starts_with('v'), ~replace_na(.,0))) %>% -->
<!--   bind_rows(summarise(., -->
<!--                       across(where(is.numeric), sum), -->
<!--                       across(where(is.character), ~"total"))) -->

<!-- DT::datatable(confidence_nw_summary, rownames= FALSE, options = list(searching = FALSE, lengthChange = FALSE, pageLength = 10)) -->

<!-- ``` -->



## Other

```{r save-session}
save.image(file = paste0("Binding_dataset_report.Rdata"))

```

